Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]

### 2013-09-13 snapshot_system/fast14_evaluation.tex
update graphs

\subsection{Deduplication Efficiency}
%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,densely dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,densely dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={5},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=88.5,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \legend{VC MH( $\sigma=4\%$),
                VC MH($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC MH(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig:exbin-efficiency-graph2}
\end{figure}

@@

\begin{table}
    \begin{tabular}{|c|c|c|c|}
    \hline
    Tasks & CPU & Mem (MB) & Disk W (MB/s) \\ \hline
    1     & 19\% & 18.1 & 32.1 \\ \hline
    2     & 35\% & 31.8 & 53 \\ \hline
    4     & 63\% & 54.1 & 84 \\ \hline
    6     & 77\% & 71.9 & 88.5 \\ \hline
    8     & 82\% & 90.5 & 89.2 \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks in each node}
\label{tab:resource_usage}
\end{table}

@@

{\bf Processing Time breakdown}.
Figure~\ref{fig:srb_vs_vc} shows
the  average  processing  time of  a VM segment under VC and SRB. 
It has a breakdown of time for reading data, updating the metadata, network latency to visit
a remote machine, and index access for fingerprint comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk, supported by a bloomer filter) 
and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS on distributed shared memory.  
SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
local meta data index.
Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/srb_vs_vc, width=3in}
  \caption{Time to backup a dirty VM segment under SRB and VC}
  \label{fig:srb_vs_vc}
\end{figure}

Figure~\ref{fig:single_vm_backup} reports the average backup time for a VM in VC when
varying the PDS size.  It lists the time distribution for data reading,
similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
While data reading dominates the backup process, PDS lookup spends about a similar amount
of time as local search.
The change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time.

\begin{figure}
    \centering
    \includegraphics[width=3in]{figures/single_backup_time}
    \caption{Average time to backup a VM in VC with varying PDS sizes}
    \label{fig:single_vm_backup}
\end{figure}

>>>>

\subsection{Deduplication Efficiency}
%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,densely dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,densely dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={2},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=85,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \legend{VC MH( $\sigma=4\%$),
                VC MH($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC MH(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig:exbin-efficiency-graph2}
\end{figure}

@@

\begin{table}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem (MB) & Write (MB/s) & Time (hrs) \\ \hline
    1     & 19\% & 18.1 & 8.37 & 1.314\\ \hline
    2     & 35\% & 31.8 & 8.97 & 1.226\\ \hline
    4     & 63\% & 54.1 & 9.33 & 1.179\\ \hline
    6     & 77\% & 71.9 & 9.46 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks in each node}
\label{tab:resource_usage}
\end{table}

@@

{\bf Processing Time breakdown}.
Figure~\ref{fig:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and SRB. 
It has a breakdown of time for reading data, updating the metadata, network latency to visit
a remote machine, and index access for fingerprint comparison.
SRB has a higher index access and fingerprint comparison because once a chunk is routed to a machine,
it relies on this local machine to access its index (often on the disk, supported by a bloomer filter) 
and perform comparison.
VC is faster for index access because it conducts in-memory local search first and then
accesses  the PDS on distributed shared memory.  
SRB spends  slighter more time in  reading data and updates because it also updates the on-disk
local meta data index.
Overall,  VC is faster than SRB, though data reading dominates the processing time for both algorithms.

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/vc_srb_combined, width=3in}
  \caption{Time to backup a dirty VM segment under SRB and VC appraoches}
  \label{fig:vc_srb_combined}
\end{figure}

% \begin{figure}[htbp]
%   \centering
%   \epsfig{file=figures/srb_vs_vc, width=3in}
%   \caption{Time to backup a dirty VM segment under SRB and VC}
%   \label{fig:srb_vs_vc}
% \end{figure}

Figure~\ref{fig:vc_srb_combined} also reports the average backup time for a VM in VC when
varying the PDS size.  It lists the time distribution for data reading,
similarity-guided local search, cross-VM PDS lookup, and non-duplicate data writing. 
While data reading dominates the backup process, PDS lookup spends about a similar amount
of time as local search.
The change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time.

% \begin{figure}
%     \centering
%     \includegraphics[width=3in]{figures/single_backup_time}
%     \caption{Average time to backup a VM in VC with varying PDS sizes}
%     \label{fig:single_vm_backup}
% \end{figure}

### 2013-09-13 snapshot_system/fast14_main.tex
update graphs

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{sansmath}
\pgfplotsset{compat=1.7}
\DeclareGraphicsExtensions{.pdf}

@@

\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup}

\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
  {wei, tyang, dagun}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix}
\usepackage{mathptmx}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{pgfplots}
\usepackage{sansmath}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

\title{Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup [draft]}

\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, and Hong Tang$^\dagger$ \\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
  \{wei, tyang, dagun\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}
